Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-11-17 tex/nusselt_paper.tex
reworks last sentence to cite keith

Future work will aim to better understand the mechanisms of shearing states and
whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  Our studies
here have set the groundwork for understanding and comparing heat transport in stratified convection
to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
convection in more realistic systems, such as those bounded by stable regions \cite{hurlburt&all1986} or 
using more realistic profiles of $\kappa$.

>>>>

Future work will aim to better understand the mechanisms of shearing states and
whether or not these states are attainable in three-dimensional, non-rotating atmospheres.  Our studies
here will serve as a foundation both for understanding and comparing heat transport in stratified convection
to that in RB convection \cite{johnston&doering2009}, and for future studies of transport in stratified
convection in more realistic systems, such as rapidly rotating atmospheres \cite{julien&all2016},
atmospheres bounded by stable regions \cite{hurlburt&all1986}, 
or regions with realistic profiles of $\kappa$.
